---
title: "DATA 606 HW 1"
output: 
  html_document: 
    toc: yes
date: "2023-01-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Question 1

```{r}
# Set seed 
set.seed(2023)

# Load packages 
library(survey)
library(sampling)
library(dplyr)
# Load data
data <- read.csv("ks-projects-201801.csv")
```

Checking the variable names and dimensions of the data

```{r}
print("Dimension of the data")
dim(data)
print("Variable names")
colnames(data)
```

The data frame has 15 columns and 378661 rows. 

## Question 2

```{r}
set.seed(2023)
# Sample 5000 indexes 
N = nrow(data) # Number of rows 
n = 5000 # Sample size
idx = sample(1:N, size = n, replace= FALSE)
samp = data[idx,]
data_sample <- data.frame(samp, pw=rep(N/n,n), fpc=rep(N,n))
svy <- svydesign(id=~0, strata= NULL, weights=~pw,data=data_sample, fpc=~fpc)
mean_sd <- svymean(~usd_pledged_real, svy)
mean_sd
```

Using a simple random sample, we get an estimated  population mean for usd_pledged_real of 8227.9 and standard deviation of 800.5.

## Question 3

```{r}
set.seed(2023)
unique(data$main_category)
table(data$main_category)
Ny = c(39874, 63585, 51918, 24602, 30070, 8809, 35231, 10819, 22816, 10913, 28153, 10779, 32569, 3768, 4755)
fpcs = round(5000*Ny/N)
idx2 = sampling::strata(data, stratanames = c("main_category"), size = fpcs, method = "srswor")
samp2 = getdata(data, idx2)

newdata2 <- data.frame(samp2, pw=rep(N/5000, 5001), fpc=c(rep(Ny[1], fpcs[1]), rep(Ny[2], fpcs[2]), rep(Ny[3], fpcs[3]), rep(Ny[4], fpcs[4]), rep(Ny[5], fpcs[5]), rep(Ny[6], fpcs[6]), rep(Ny[7], fpcs[7]), rep(Ny[8], fpcs[8]), rep(Ny[9], fpcs[9]), rep(Ny[10], fpcs[10]), rep(Ny[11], fpcs[11]), rep(Ny[12], fpcs[12]), rep(Ny[13], fpcs[13]), rep(Ny[14], fpcs[14]), rep(Ny[15], fpcs[15])))
svy2 <- svydesign(id=~1, strata = ~main_category, weights=~pw,data = newdata2, fpc=~fpc)
mean_sd2 = svymean(~usd_pledged_real, svy2)
mean_sd2
```

Using a stratified sample, we get an estimated population mean for usd_pledged_real of 8567.8 and a standard deviation 844.22.

## Question 4

```{r}
set.seed(2023)
idx3<-sampling:::cluster(data, clustername = "country", size = 2, method = "srswor")
clus<-getdata(data, idx3)
length(unique(data$country))
clus$pw=rep(23/2,dim(clus)[1])
unique(clus$country)
nrow(clus[clus$country == "FR",]) + nrow(clus[clus$country == "LU",])
clus$fpc = c(rep(23, 3001))


scluster<-svydesign(id=~country, weights=~pw, data = clus, fpc=~fpc)
mean_sd3<-svymean(~usd_pledged_real, scluster)
mean_sd3
```

Using a clustered sample, we get an estimated population mean for usd_pledged_real of 11605 and a standard deviation of 159.73.

## Question 5

```{r}
ratio<-svyratio(~usd_pledged_real, ~usd_goal_real, svy)
ratio

# Predicted 500k
pred1<-predict(ratio, 500000)
# Predicted 1000k
pred2<-predict(ratio, 1000000)
# Predicted 2000k
pred3<-predict(ratio, 2000000)

pred1
pred2
pred3
```

We get an estimated ratio of 0.1718 with a standard deviation of 0.07391.

**For Goal amount of 500k:**
Predicted USD Pledged: 85899.85
Standard Deviation: 36955.69


**For Goal amount of 1000k:**
Predicted USD Pledged: 171799.7
Standard Deviation: 73911.39

**For Goal amount of 2000k:**
Predicted USD Pledged: 343599.4
Standard Deviation: 147822.8


**Session Info**
```{r}
sessionInfo()
```

