---
title: "DATA 606 HW 2"
output: 
  pdf_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
```{r}
library(mlbench)
data(PimaIndiansDiabetes)
data <- PimaIndiansDiabetes
dim(data)
colnames(data)
summary(data$diabetes) # 2 levels (neg: 500, pos: 268)
# Check how R dummifies the diabetes variable
```

## Question 2
```{r}
library(ISLR)
library(car)
set.seed(10)
train_index <- c(sample(which(data$diabetes == "neg"), 400), sample(which(data$diabetes == "pos"), 200))

train_df <- data[train_index,]
test_df <- data[-train_index,]

model_fit<-glm(diabetes~pregnant+glucose+pressure+triceps+insulin+mass+pedigree+age, family=binomial, data=train_df)
summary(model_fit)
```

**Pressure** and **Insulin** contribute negatively to the "pos" result.


```{r}
vif(model_fit)
```
I do not detect any multicollinearity as all vif values are between 1 and 1.6.

## Question 3
```{r}
prediction <- predict(model_fit, test_df, type="response")
dia.predict=rep("neg",168)
dia.predict[prediction>=0.5]="pos"
actual=test_df$diabetes
matrix <- table(dia.predict,actual)
paste("Misclassification Rate:", (matrix[1,2] + matrix[2,1])/sum(matrix)*100,"%")
```


## Question 4

Age, Triceps and Insulin are all not statistcally different from 0 using a significance level of 0.

```{r}
model_fit2<-glm(diabetes~pregnant+glucose+pressure+mass+pedigree, family=binomial, data=train_df)
summary(model_fit2)
```
```{r}
prediction <- predict(model_fit2, test_df, type="response")
dia.predict=rep("neg",168)
dia.predict[prediction>=0.5]="pos"
actual=test_df$diabetes
matrix <- table(dia.predict,actual)
paste("Misclassification Rate:", (matrix[1,2] + matrix[2,1])/sum(matrix)*100,"%")
```


## Question 5
```{r}
library(MASS)
lda.fit<-lda(diabetes~pregnant+glucose+pressure+triceps+insulin+mass+pedigree+age, data=train_df)
lda.pred=predict(lda.fit, test_df)
matrix <- table(lda.pred$class, test_df$diabetes)
paste("Misclassification Rate:", (matrix[1,2] + matrix[2,1])/sum(matrix)*100,"%")
```


## Question 6
```{r}
combos <- c("Pregnant, Glucose", "Pregnant, Mass", "Pregnant, Pedigree", "Glucose, Mass", "Glucose, Pedigree", "Mass, Pedigree")
misclass_rates <- c()

lda.fit<-lda(diabetes~pregnant+glucose, data=train_df)
lda.pred=predict(lda.fit, train_df)
matrix <- table(lda.pred$class, train_df$diabetes)
misclass_rates[1] <- (matrix[1,2] + matrix[2,1])/sum(matrix)*100

misclass_rates
lda.fit<-lda(diabetes~pregnant+mass, data=train_df)
lda.pred=predict(lda.fit, train_df)
matrix <- table(lda.pred$class, train_df$diabetes)
misclass_rates[2] <- (matrix[1,2] + matrix[2,1])/sum(matrix)*100

lda.fit<-lda(diabetes~pregnant+pedigree, data=train_df)
lda.pred=predict(lda.fit, train_df)
matrix <- table(lda.pred$class, train_df$diabetes)
misclass_rates[3] <- (matrix[1,2] + matrix[2,1])/sum(matrix)*100

lda.fit<-lda(diabetes~glucose+mass, data=train_df)
lda.pred=predict(lda.fit, train_df)
matrix <- table(lda.pred$class, train_df$diabetes)
misclass_rates[4] <- (matrix[1,2] + matrix[2,1])/sum(matrix)*100

lda.fit<-lda(diabetes~glucose+pedigree, data=train_df)
lda.pred=predict(lda.fit, train_df)
matrix <- table(lda.pred$class, train_df$diabetes)
misclass_rates[5] <- (matrix[1,2] + matrix[2,1])/sum(matrix)*100

lda.fit<-lda(diabetes~pedigree+mass, data=train_df)
lda.pred=predict(lda.fit, train_df)
matrix <- table(lda.pred$class, train_df$diabetes)
misclass_rates[6] <- (matrix[1,2] + matrix[2,1])/sum(matrix)*100

misclass_combos <- data.frame(combos, misclass_rates)
misclass_combos
```

From the data frame above, the combination of glucose and mass variables create the lowest misclassification rate at 23.5%. 

```{r}
lda.fit2 <- lda(diabetes~glucose+mass, data=train_df)
lda.pred=predict(lda.fit2, test_df)
matrix <- table(lda.pred$class, test_df$diabetes)
paste("Misclassification Rate:", (matrix[1,2] + matrix[2,1])/sum(matrix)*100,"%")
```

## Question 7
```{r}
qda.fit<-qda(diabetes~pregnant+glucose+pressure+triceps+insulin+mass+pedigree+age, data=train_df)
qda.pred=predict(qda.fit, test_df)
matrix <- table(qda.pred$class, test_df$diabetes)
paste("Misclassification Rate:", (matrix[1,2] + matrix[2,1])/168*100,"%")
```

Using Quadratic Discriminant Analysis increases the misclassification rate.